Results

### 2025-04-14 notebooks/00_index.qmd
feat: anisotry plot

```{julia}
using Speasy
using SPEDAS
using SPEDAS: ulabel, smooth
using DimensionalData
using GLMakie
using Statistics
# using CairoMakie
using Dates
using PartialFunctions
using Unitful
using Beforerr: _theme_legend
using SPEDAS.SpaceDataModel: set
using PSPAnisotropy
include("../src/psp_temp.jl")
using PSPAnisotropy: Wind, PSP, THEMIS

@@

mva_transform((V, B), tmin, tmax) = mva(V(tmin, tmax), B(tmin, tmax))
```

```{julia}
tmin_psp = DateTime("2021-01-14")
tmax_psp = DateTime("2021-01-21")
tmin_wind = DateTime("2021-01-15")
tmax_wind = DateTime("2021-01-23")
tmax_wind = DateTime("2021-02-15")

@@

B_ylabel = "B (nT)"
B_labels = ["Bx", "By", "Bz", "Magnitude"]
n_ylabel = ulabel("Density", "cm^-3")
V_ylabel = "Velocity (km/s)"
V_labels = ["Vx", "Vy", "Vz", "Magnitude"]
Temp_ylabel = "Temperature (eV)"

@@

```{julia}
B = PSP.B(tmin_psp, tmin_psp + Hour(1))
V = PSP.V(tmin_psp, tmin_psp + Hour(1))
current_density(B, V)
```

@@

```{julia}
tvars_wind = [
    tnorm_combine ∘ Wind.B,
    Wind.n,
    # tsubtract ∘ SpeasyProduct("WI_K0_SWE_RTN/V_RTN"; ylabel=V_ylabel, labels=V_labels),
    tsubtract ∘ Wind.V,
    wind_temp
]
```

```{julia}
tvars_themis = [
    tnorm_combine ∘ THEMIS.B,
    THEMIS.n,
    THEMIS.V_GSE,
    THEMIS.T,
]
```

@@

```{julia}
using Discontinuity

tau = Second(30)
# psp_events = detect_variance(PSP.B, tmin_psp, tmax_psp, tau)
# wind_events = detect_variance(Wind.B, tmin_wind, tmax_wind, tau)
thm_events = detect_variance(Wind.B, tmin_wind, tmax_wind, tau; split=Day(1))
```

@@

wind_B_mva = set(mva ∘ Wind.B; name="mva_B", labels=B_mva_labels)
wind_V_mva = Product((Wind.V_GSE, Wind.B_GSE), mva_transform; ylabel=V_ylabel, labels=V_mva_labels)
wind_mva_all = [wind_B_mva, wind_V_mva, Wind.Temp_ani]

@@

```{julia}
using DataFrames

@kwdef struct Event
    start
    stop
    metadata = Dict()
end

Event(df::DataFrame, i) = Event(df.tstart[i], df.tstop[i], Dict())

(P::AbstractProduct)(e::Event) = P(e.start, e.stop)
```

```{julia}
function plot_candidate(f, event, ts, toffset=Second(0); kwargs...)
    tplot(f, ts, event.tstart - toffset, event.tstop + toffset; kwargs...)
end

let link_xaxes = false
    tvars_wind = [
        tnorm_combine ∘ Wind.B,
        Wind.n,
        Wind.V_GSE,
        Wind.temp,
        wind_B_mva,
        wind_V_mva,
        Wind.Temp_ani
    ]

    tvars_themis2 = [[THEMIS.B_FGL_GSE, THEMIS.n, THEMIS.V_GSE, THEMIS.T]; thm_mva_all]

    f = Figure(; size=(1200, 800))
    plot_candidate(f[1, 1], Event(psp_events, 2), [tvars_psp; psp_mva_all]; link_xaxes)
    wind_plots = plot_candidate(f[1, 2], Event(wind_events, 3), tvars_wind, Minute(1); link_xaxes)
    themis_plots = plot_candidate(f[1, 3], Event(thm_events, 3), tvars_themis2, Minute(1); link_xaxes)
    # hideydecorations!(wind_plots)
    # hideydecorations!(themis_plots)
    f
end
```

>>>>

```{julia}
using Speasy
using SPEDAS
using SPEDAS: ulabel, smooth
using DimensionalData
using GLMakie
using Statistics
# using CairoMakie
using Dates
using PartialFunctions
using Unitful
using Beforerr: _theme_legend
using SPEDAS.SpaceDataModel: set, extend, @set
using PSPAnisotropy
include("../src/psp_temp.jl")
include("../src/calc.jl")
using PSPAnisotropy: Wind, PSP, THEMIS

@@

mva_transform((V, B), tmin, tmax; tb_min=tmin, tb_max=tmax) = mva(V(tmin, tmax), B(tb_min, tb_max))
make_mva_transform(tb_min, tb_max) = mva_transform$(; tb_min, tb_max)

j_transform((V, B), tmin, tmax) = current_density(B(tmin, tmax), V(tmin, tmax))
```

```{julia}
tmin_psp = DateTime("2021-01-14")
tmax_psp = DateTime("2021-01-21")
tmin_wind = DateTime("2021-01-15")
tmax_wind = DateTime("2021-01-23")

@@

B_ylabel = "B (nT)"
B_labels = ["Bx", "By", "Bz", "Magnitude"]
n_ylabel = ulabel("Density", "cm^-3")
V_ylabel = "V (km/s)"
ΔV_ylabel = "ΔV (km/s)"
V_labels = ["Vx", "Vy", "Vz", "Magnitude"]
Temp_ylabel = "Temperature (eV)"

@@

@@

```{julia}
tvars_wind = [
    tnorm_combine ∘ Wind.B,
    Wind.n,
    # tsubtract ∘ SpeasyProduct("WI_K0_SWE_RTN/V_RTN"; ylabel=V_ylabel, labels=V_labels),
    tsubtract ∘ Wind.V,
    Wind.temp
]
```

```{julia}
tvars_themis = [
    tnorm_combine ∘ THEMIS.B_GSE,
    THEMIS.n,
    THEMIS.V_GSE,
    THEMIS.T,
]
```

@@

```{julia}
using Discontinuity
tau = Second(30)
# psp_events = detect_variance(PSP.B, tmin_psp, tmax_psp, tau)
wind_events = ids_finder(Wind.B, tmin_wind, tmax_wind, tau)
# thm_events = detect_variance(Wind.B, tmin_wind, tmax_wind, tau; split=Day(1))
```

@@

@@

```{julia}
function make_mva_product(event, V, B=V; kwargs...)
    mva_transform = make_mva_transform(t_us_ds(event)...)
    return Product((V, B), mva_transform; kwargs...)
end

function make_mva_products(event, B, V, n=nothing, T3=nothing)
    B_mva = make_mva_product(event, B, B; labels=B_mva_labels, ylabel=B_ylabel)
    V_mva = make_mva_product(event, V, B; labels=V_mva_labels, ylabel=V_ylabel)
    J = Product((V_mva, B_mva), j_transform)
    result = [tnorm_combine ∘ B, V, B_mva, set(tsubtract ∘ V_mva; ylabel=ΔV_ylabel), J]
    isnothing(n) || push!(result, set(
        tsubtract ∘ Product((B_mva, n), alfven_velocity_ts);
        ylabel=ΔV_ylabel, labels=["Va_L", "Va_M", "Va_N"]
    ))
    isnothing(T3) || begin
        Λ = Product((B_mva, n, T3), anisotropy_ts; ylabel="Λ")
        Va_Λ = set(
            tsubtract ∘ Product((B_mva, n, T3), alfven_velocity_ani_ts);
            ylabel=ΔV_ylabel, labels=["Va*_L", "Va*_M", "Va*_N"]
        )
        push!(result, Λ, Va_Λ)
    end
    return result
end
```

```{julia}
tvars2_wind = [
    tnorm_combine ∘ Wind.B,
    Wind.n,
    Wind.V_GSE,
    Wind.temp,
    Wind.Temp_ani
]

tvars_themis2 = [[THEMIS.B_FGL_GSE, THEMIS.n, THEMIS.V_GSE, THEMIS.T]; thm_mva_all]
```

```{julia}
function plot_candidate(f, event, ts, toffset=Second(0); kwargs...)
    tmin, tmax = t_us_ds(event)
    f = tplot(f, ts, tmin - toffset, tmax + toffset; kwargs...)
    tlines!(f, [tmin, tmax])
    f
end

f = let
    f = Figure(; size=(1200, 800))
    # plot_candidate(f[1, 1], Event(psp_events, 2), [tvars_psp; psp_mva_all]; link_xaxes)

    wind_event = Event(wind_events, 9) # 300
    wind_T3 = extend(Wind.pTemp_ani, Second(20))
    wind_tvars = make_mva_products(wind_event, Wind.B_GSE, Wind.V_GSE, Wind.n_p, wind_T3)
    wind_tvars = [wind_tvars[3:end]; Wind.Temp_ani; Wind.n; Wind.Temp]
    for p in Wind.Temp_ani
        @info "$p" data = p(wind_event)
    end
    wind_plots = plot_candidate(f, wind_event, wind_tvars, tau)
    # themis_plots = plot_candidate(f[1, 3], Event(thm_events, 3), tvars_themis2, Minute(1); link_xaxes)
    # hideydecorations!(wind_plots)
    # hideydecorations!(themis_plots)
end
```
